\documentclass[letter,titlepage,oneside,english]{report}
\usepackage[margin=1in]{geometry}

% Locale and encoding
\usepackage{csquotes}
\usepackage{babel}

\title{
  Team 13: Phase I\\
  SE 4352.001
}
\author{%
  Hoang, Kelly\\
  kkh150130\\[3ex]
  Mitash, Jacob\\
  jsm150030
  \and
  LaFreniere, Joseph\\
  jml140230\\[3ex]
  Mitchell, Daniel\\
  dxm115030
}
\date{2017-09-21}

\usepackage{enumitem}
% Environment for functional requirements
\newlist{fr}{enumerate}{10}
\setlist[fr,1]{label=FR\,\arabic*}
\setlist[fr]{label*=.\arabic*}
% Environment for non-functional requirements
\newlist{nfr}{enumerate}{10}
\setlist[nfr,1]{label=NFR\,\arabic*}
\setlist[nfr]{label*=.\arabic*}

% %%%%%%%%
\begin{document}

\maketitle{}

The goal of this project is to develop a smart home application system that will be used in multiple home properties (henceforth \enquote{properties}) in order to ensure a secure and comfortable living style for the guests.
This project will provide for greater safety and convenience of property landlords and tenants through surveillance, tracking, and automation of parts of the properties.
This project will assist property owners in remotely managing their properties, including managing the levels of access each property manager and tenant has in order to establish a successful rental property business.

\begin{fr}
\item
  The system shall require that a user have authorization to perform a given task before allowing that user to perform the task.
  \begin{fr}
  \item
    The system shall allow a property's owner to appoint one or more managers to the property.
  \item
    The system shall allow a property's owner or manager to create other users and assign those users authorization levels.
  \item
    The system shall require that users provide some means of authentication to verify their identities.
    \begin{fr}
    \item
      RFID keycards shall be an accepted means of authentication.
      \begin{fr}
      \item
        Guests shall be permitted to keep a keycard after the expiration of their lease.
        In such cases the guests' access will have already been revoked pending the signing of a new lease.
      \end{fr}
    \item
      Verified biometrics shall be an accepted means of authentication.
    \end{fr}
  \end{fr}
\item
  The system shall interact with external, Internet-facing services and devices.
  \begin{fr}
  \item\label{fr:external:weather}
    The system shall incorporate local sensors and data from Internet-based weather services to make weather- and temperature-dependent decisions.
  \end{fr}
\item
  The system shall monitor devices internal to it.
  \begin{fr}
  \item
    The system shall monitor the amount of food in the refrigerator.
    \begin{fr}
    \item
      The system shall be able to determine when the refrigerator is empty.
    \end{fr}
  \item\label{fr:internal:smoke_detector}
    The system shall monitor properties' smoke detectors.
  \end{fr}
\item
  The system shall restrict physical access to the properties to authorized users.
  \begin{fr}
  \item
    The system shall allow a property's owner unrestricted access to the property.
  \item
    The system shall allow a property's manager unrestricted access to the property.
  \item
    The system shall allow a property's owner or manager to schedule per-door access for other users.
  \item
    The system shall allow a property's current lease-holding guest to schedule per-door access for other current guests.
  \end{fr}
\item\label{fr:controls}
  The system shall expose digital controls for certain aspects of its managed properties.
  \begin{fr}
  \item\label{fr:customizable}
    The following aspects shall be controllable by lease-holding guests:
    \begin{fr}
    \item
      the hue of artificial lighting
    \item
      the brightness of artificial lighting
    \item
      the window blinds
    \end{fr}
  \item\label{fr:customizable:request}
    In addition to the property aspects listed in~\ref{fr:customizable}, the system shall allow lease-holding guests to request access to the following aspects:
    \begin{fr}
    \item
      the indoor temperature
    \item
      the dish washer
    \item
      the stove
    \item
      the oven
    \end{fr}
  \item\label{fr:customizable:request_approve}
    The system shall allow a property's owner or manager to approve guests' requests as placed per~\ref{fr:customizable:request}.
  \item\label{fr:customizable:multiple_profiles}
    The system shall allow users to have multiple preference profiles for a single object.
  \item
    The system shall allow users to schedule the application of profiles from \ref{fr:customizable:multiple_profiles}.
  \item
    The system shall provide physical overrides for automated aspects of the system.
  \end{fr}
\item\label{fr:software}
  The system's software components shall be accessible over the Internet.
  \begin{fr}
  \item\label{fr:software:ui}
    The system shall present a graphical user interface (GUI) to its end users.
    \begin{fr}
    \item\label{fr:software:ui:devices}
      The system's GUI shall support the following classes of devices:
      \begin{fr}
      \item
        smartphone
      \item
        laptop
      \item
        desktop
      \item
        tablet
      \end{fr}
    \end{fr}
  \item\label{fr:software:fridge}
    The system shall allow a property's guests to remotely view the contents of that property's refrigerator.
  \end{fr}
\item
  The system shall allow users to set personal preferences for property configuration.
  \begin{fr}
  \item
    Persistent preferences shall be available for the aspects listed in \ref{fr:customizable}.
  \item
    Users shall customize their preference profiles manually.
  \item\label{fr:config:control_panel}
    The system shall provide a digital preferences control panel.
    \begin{fr}
    \item\label{fr:config:control_panel:devices}
      \ref{fr:config:control_panel} shall be accessible from the devices listed in \ref{fr:software:ui:devices}.
    \end{fr}
  \item
    The system shall persist the user preferences and maintain them for any subsequent properties that have not already had preference profiles manually set.
  \item
    The system shall allow property owners and managers to determine which aspects of their property guests may set preferences for.
  \item\label{fr:preferences:order}
    The system shall apply the user preferences of the user with the highest role (as described in the following list) when there are conflicting preferences.
    \begin{enumerate}
    \item
      Owner
    \item
      Manager
    \item
      Lease-holding guest
    \item
      Non-lease-holding guest
    \item
      Maintenance staff
    \end{enumerate}
  \item
    The system shall apply the average of the highest ranking users' preferences when multiple users of the highest role have conflicting preferences.
  \end{fr}
\item
  The system shall allow for video and audio observation of properties.
  \begin{fr}
  \item
    Recording shall be motion-activated.
  \item
    Recorded data shall be cached onsite.
  \item
    Recorded data shall be uploaded offsite as the network permits.
  \item
    If recordings were taken at a property while a guest held a lease at that property, viewing of the recordings shall require the permission of the guest given in a legally-binding manner or a court order.
  \item
    A property's lease-holding guest shall have viewing access to recordings taken at the property during the time of the guest's lease.
  \item
    A lease-holding guest shall be able to disable video or audio recordings of the property they are renting.
    \begin{fr}
    \item
      If a lease-holding guest disables video or audio recording, the date and time at which the recording stops shall be recorded.
    \item
      If a lease-holding guest disables video or audio recording, the duration of time during which the recording was disabled shall be recorded.
    \end{fr}
  \end{fr}
\item
  The system shall provide WLAN access at each property.
  \begin{fr}
  \item
    Connecting a device to a property's WLAN shall require that the device be authenticated by an owner, manager, guest, or staff member of the property.
  \end{fr}
\item
  The system shall be capable of sending notifications to user's electronic devices.
  \begin{fr}
  \item
    The devices supported for notification receipt shall include (but not be limited to) the devices listed in \ref{fr:software:ui:devices}.
  \item
    The property owner and managers shall be notified if the system detects that one of its devices needs servicing.
  \item
    A property's lease-holding guest shall be notified if the system detects that the property's fridge is low on food.
  \item
    A property's owner, managers, guests, and maintenance staff shall be notified if the property's smoke detector senses any smoke.
  \item
    If data collected in \ref{fr:external:weather} indicates ongoing or imminent severe weather at a property, a notification will be sent to the owner, managers, and guests of that property.
  \end{fr}
\end{fr}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
